Two NIRCam channels are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-10-04 ms.tex
I corrected the second order overlap range to 2.0 to 2.02 as well as introduced the APT acroynm.

No single JWST instrument can measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum.
The largest bandwidths possible are NIRSpec's low resolution double prism ($0.7-5.0~\mu$m) and MIRI's low resolution prism (LRS; $5-12~\mu$m).
Unfortunately, NIRSpec's low resolution prism mode is so sensitive that it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planetary systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits:\ one with NIRISS SOSS (\SOSSrange), two with NIRCam's long-wavelength channel grisms (F322W2 and F444W + grisms; $2.44-4.98~\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H modes ($1.7-5.0~\mu$m.} and one with MIRI LRS ($5-12~\mu$m).
Using the Astronomer's Proposal Tool software\footnote{http://www.stsci.edu/hst/proposing/apt}, each transit observation (pre-ingress, transit, and post-ingress) requires $\sim$9~hours and incurs overheads of $\sim$2~hours, resulting in a total of $\sim$11~hours per transit and hence $\sim$44~hours total to cover
the full wavelength range.

The NIRCam instrument is primarily an imager, but it includes several spectroscopic modes originally designed for observatory wavefront sensing.
These include the grisms installed in its long-wavelength channel as well as the Dispersed Hartmann Sensors (DHSs) installed in its short-wavelength channel.
The long-wavelength grisms are used in concert with broadband filters.
The F322W2 filter covers 2.44$\mu$m to 4.02$\mu$m half maximum throughput while the F444W filter covers 3.88$\mu$m to 4.98$\mu$m at half maximum throughput.
These filters and grism are enabled and supported JWST science modes.
The DHS would be used primarily with the F150W2 filter, which covers from 1.01$\mu$m to 2.35$\mu$m at half maximum throughput.
The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the second order of the spectrum begins to overlap at 2.0$\mu$m.\footnote{The prisms that spatially separate the 10 DHS spectra cross-disperse the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
When using the DHS with the F150W2 filter and pairing it with the long wavelength grisms (F322W2 and F444W), the wavelength coverage will therefore be 1.0 to 5.0$\mu$m with a gap from 2.00$\mu$m to 2.44$\mu$m.
This wavelength gap can include a CH$_4$ feature for cool planets, but other CH$_4$ bands are also visible at 1.7$\mu$m and 3.5$\mu$m.

>>>>

No single JWST instrument can measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum.
The largest bandwidths possible are NIRSpec's low resolution double prism ($0.7-5.0~\mu$m) and MIRI's low resolution prism (LRS; $5-12~\mu$m).
Unfortunately, NIRSpec's low resolution prism mode is so sensitive that it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planetary systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits:\ one with NIRISS SOSS (\SOSSrange), two with NIRCam's long-wavelength channel grisms (F322W2 and F444W + grisms; $2.44-4.98~\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H modes ($1.7-5.0~\mu$m.} and one with MIRI LRS ($5-12~\mu$m).
Using the Astronomer's Proposal Tool (APT) software\footnote{http://www.stsci.edu/hst/proposing/apt}, each transit observation (pre-ingress, transit, and post-ingress) requires $\sim$9~hours and incurs overheads of $\sim$2~hours, resulting in a total of $\sim$11~hours per transit and hence $\sim$44~hours total to cover
the full wavelength range.

The NIRCam instrument is primarily an imager, but it includes several spectroscopic modes originally designed for observatory wavefront sensing.
These include the grisms installed in its long-wavelength channel as well as the Dispersed Hartmann Sensors (DHSs) installed in its short-wavelength channel.
The long-wavelength grisms are used in concert with broadband filters.
The F322W2 filter covers 2.44$\mu$m to 4.02$\mu$m half maximum throughput while the F444W filter covers 3.88$\mu$m to 4.98$\mu$m at half maximum throughput.
These filters and grism are enabled and supported JWST science modes.
The DHS would be used primarily with the F150W2 filter, which covers from 1.01$\mu$m to 2.35$\mu$m at half maximum throughput.
The range from 2.02$\mu$m to 2.35$\mu$m will probably be discarded because the second order of the spectrum begins to overlap at 2.0$\mu$m.\footnote{The prisms that spatially separate the 10 DHS spectra cross-disperse the second order spectrum by 0 to 15 pixels, so the contamination can be reduced in some cases.}
When using the DHS with the F150W2 filter and pairing it with the long wavelength grisms (F322W2 and F444W), the wavelength coverage will therefore be 1.0 to 5.0$\mu$m with a gap from 2.00$\mu$m to 2.44$\mu$m.
This wavelength gap can include a CH$_4$ feature for cool planets, but other CH$_4$ bands are also visible at 1.7$\mu$m and 3.5$\mu$m.
